CF Registry Analysis

### 2022-12-12 Christine Chan/CF Registry/cf_registry_analysis.Rmd
might need to start over...
registry on last section

  emp <- r[paste0("employment", 1:7)]
  emp <- as.numeric(emp)
  if (all(is.na(emp) | emp == 0)) {

@@

    emp <- as.numeric(emp)
    emp <- which(emp == 1)

@@

df$employment <- sub("1", "Part Time", df$employment)
df$employment <- sub("2", "Full time homemaker", df$employment)
df$employment <- sub("3", "Full time employment", df$employment)
df$employment <- sub("4", "Unemployed", df$employment)
df$employment <- sub("5", "Student", df$employment)
df$employment <- sub("6", "Disabled", df$employment)
df$employment <- sub("7", "Retired", df$employment)
df$employment <- as.factor(df$employment)

@@

  bronch <- r[grep("bronchodilators",names(r))]

@@

@@

@@

```{r warning=FALSE,results='asis'}
# Summarize by ID and period
t2_df <- df %>%
  group_by(eDWID, Period) %>%
  summarise(
    Smoking = max(smoking,na.rm = T),
    `Secondhand smoke`=max(second_smoke,na.rm = T),
    `FEV1 % Predicted` = last(na.omit(GLI_FEV1_pct_predicted)),
    `FVC % Predicted` = last(na.omit(GLI_FVC_pct_predicted)),
    `Pulm. Exacerbations` = last(na.omit(NumPulmExacerbation)),
    .groups = "keep"
  )
# Replace infinite values with missing
# t2_df <- data.frame(lapply(t2_df, function(c) {
#   c[is.infinite(c)] <- NA
#   return(c)
# }))
# Print table 1
cols <- colnames(t2_df)[3:ncol(t2_df)]
t2 <- tableby(as.formula(paste0("Period~", paste0("`", cols, "`", collapse = "+"))),
  data = t2_df
)
summary(t2)
```

>>>>

  emp <- r[paste0("employment",1:7)]
  emp = as.numeric(emp)
  names(emp) = c("Part Time",
                    "Full time homemaker",
                    "Full time employment",
                    "Unemployed",
                    "Student",
                    "Disabled",
                    "Retired"
  if (all(is.na(emp))) {

@@

    emp <- names(emp)[which(emp == 1)]

@@

@@

  bronch <- r[grep("A_bronchodilators",names(r))]
  bronch = as.numeric(bronch)

@@

  act = as.numeric(act)

@@

df$F508del = (df$Mutation1 =="F508del") + (df$Mutation2=="F508del")
df$F508del = factor(df$F508del,levels = 0:2,labels = c("None","Heterozygous","Homozygous"))
# Yes/no variables
df$A_IsOnEnzymes = factor(df$A_IsOnEnzymes,levels = 0:1,labels = c("No","Yes"))
df$A_salt_supplement = factor(df$A_salt_supplement,levels = 0:1,labels = c("No","Yes"))
df$A_cf_vitamins = factor(df$A_cf_vitamins,levels = 0:1,labels = c("No","Yes"))
df$A_dornasealfa = factor(df$A_dornasealfa,levels = 0:1,labels = c("No","Yes"))
df$A_pulmonarycomplications4 = factor(df$A_pulmonarycomplications4,
                                      levels = 0:1,labels = c("No","Yes"))
df$A_pulmonarycomplications5 = factor(df$A_pulmonarycomplications5,
                                      levels = 0:1,labels = c("No","Yes"))
df$A_othercomplications9 = factor(df$A_othercomplications9,
                                      levels = 0:1,labels = c("No","Yes"))
df$A_hepatobiliary1_3 = factor(df$A_hepatobiliary1_3,
                                      levels = 0:1,labels = c("No","Yes"))

@@

```{r warning=FALSE,results='asis'}
# Summarize by ID and period
t2_df <- df %>%
  group_by(eDWID, Period) %>%
  summarise(
    Smoking = max(smoking,na.rm = T),
    `Secondhand smoke`=max(second_smoke,na.rm = T),
    `FEV1 % Predicted` = last(na.omit(GLI_FEV1_pct_predicted)),
    `FVC % Predicted` = last(na.omit(GLI_FVC_pct_predicted)),
    `Pulm. Exacerbations` = last(na.omit(NumPulmExacerbation)),
    `Bronchodilator` = last(na.omit(bronchodilators)),
    `Primary ACT` = last(na.omit(act_primary)),
    `Oxygen Therapy` = last(na.omit(oxygen_therapy)),
    .groups = "keep"
  )
# Replace infinite values with missing
# t2_df <- data.frame(lapply(t2_df, function(c) {
#   c[is.infinite(c)] <- NA
#   return(c)
# }))
# Print table 1
cols <- colnames(t2_df)[3:ncol(t2_df)]
t2 <- tableby(as.formula(paste0("Period~", paste0("`", cols, "`", collapse = "+"))),
  data = t2_df
)
summary(t2)
```

# Table 3: Panreactic function

```{r warning=FALSE,results='asis'}
# Summarize by ID and period
t3_df <- df %>%
  group_by(eDWID, Period) %>%
  summarise(
    `On Enzymes` = last(na.omit(A_IsOnEnzymes)),
    `Mutation Class` = last(na.omit(MutClass)),
    `F508del`=last(na.omit(F508del)),
    .groups = "keep"
  )
# Replace infinite values with missing
# t3_df <- data.frame(lapply(t3_df, function(c) {
#   c[is.infinite(c)] <- NA
#   return(c)
# }))
# Print table 1
cols <- colnames(t3_df)[3:ncol(t3_df)]
t3 <- tableby(as.formula(paste0("Period~", paste0("`", cols, "`", collapse = "+"))),
  data = t3_df
)
summary(t3)
```

# Table 4: Nutrition

```{r warning=FALSE,results='asis'}
# Summarize by ID and period
t4_df <- df %>%
  group_by(eDWID, Period) %>%
  summarise(
    `BMI %ile` = last(na.omit(A_bmipercentile)),
    `Salt Supplement` = max(A_salt_supplement,na.rm = T),
    `CF Vitamins` = max(A_cf_vitamins,na.rm = T),
    `Hemoptysis` = max(A_pulmonarycomplications4,na.rm = T),
    `Pneumothorax Chest Tube` = max(A_pulmonarycomplications5,na.rm = T),
    `Sinus Disease` = max(A_othercomplications9,na.rm = T),
    `Cirrhosis` = max(A_hepatobiliary1_3,na.rm = T),
    .groups = "keep"
  )
# Replace infinite values with missing
# t4_df <- data.frame(lapply(t4_df, function(c) {
#   c[is.infinite(c)] <- NA
#   return(c)
# }))
# Print table 1
cols <- colnames(t4_df)[3:ncol(t4_df)]
t4 <- tableby(as.formula(paste0("Period~", paste0("`", cols, "`", collapse = "+"))),
  data = t4_df
)
summary(t4)
```
